STAT 133 Final Project: Visualizing Berkeley Police Data

### 2016-08-10 final_paper/STAT 133 Final Project_ Visualizing Berkeley Police Data.Rmd
html~

---
title: "STAT 133 Final Project: Visualizing Berkeley Police Data"
author: "Amy Zhu, Mengyu Li, Rebecca Reus, and Shangjun Jiang"
date: "9 August 2016"
output: 
    pdf_document:
    latex_engine: xelatex
    fig_caption: yes
    keep_tex: yes
header-includes: \usepackage{float}
sansfont: Times New Roman

---

>>>>

---
title: 'STAT 133 Final Project: Visualizing Berkeley Police Data'
author: "Amy Zhu, Mengyu Li, Rebecca Reus, and Shangjun Jiang"
date: "9 August 2016"
output:
  html_document: default
  fig_caption: yes
  keep_tex: yes
  latex_engine: xelatex
  pdf_document: null
sansfont: Times New Roman
header-includes: \usepackage{float}
---
